Title here

### 2016-12-22 portfolio/text/ms.Rmd
Editing

@@

Our results provide additional support for the idea that individual fishers can
reduce their income variability by diversifying their catch portfolios. However,
most individuals do not appear to change their catch diversity substantially
from year to year [OLE: is there a supplemental figure or statistic that speaks
to this point?], and most strategies adopted by Alaskan fishermen lie in
a high-risk, high-reward quadrant in which reducing diversification increases
both revenue variability and expected revenue. Previous work has suggested that
changes to fisheries management such as limited entry or catch share programs
may inadvertently act as barrier to diversification and promote specializing
(Hilborn et al. 2003; Kasperski and Holland 2013). While some of these
specialized fishing strategies may be associated with increased revenue
variability, the benefit may be that they are also associated with increased
revenue.

@@

Our findings across fishing strategies are in line with previous findings
[@kasperski2013, @sethi2012b, @sethi2014], but we also found that, for
individuals, specializing tended to be associated with increased revenue and
altering species diversity tended to be associated with increased revenue
variability. Specializing has been shown to be profitable in some circumstances
for other natural resource sectors. For example, while diversification is
generally helpful for small-scale farmers, farmers that specialize on
high-demand and high-value crops such as tobacco or cocoa can benefit, at least
in the short term, from specializing on these crops (REF). In terms of variance,
there are number of reasons by annual revenue variability might be expected to
increase with changes to individual fished species diversity. First, changes to
fishing patterns will sometimes be associated with a learning or adaptation
phase as individuals become accustomed to new locations, new gear, or new
species. Secondly, changes in diversity might reflect years in which targeted
species were less available and fishers were forced to target other species or
landed more bycatch. Most importantly, this increased variability technically
reflects an inability for our large-scale model to predict an individual's
revenue in a subsequent year. There are many reasons, often unique to an
individual permit holder and therefore not included in a large-scale model, that
might make that specific individual's revenue less predictable given a change in
species diversity compared to not changing species diversity from one year to
the next.

@@

Our analysis provides a synthetic view of the effects of species diversity on
individuals over 30 years in one of the most productive fishing regions in the
world. However, our analysis simultaneously uses data from across the broad
geography of Alaska and over 30 years, potentially obscuring regional or
time-variation in the consequences of diversification on revenue and revenue
variability. We expect future research examining diversification over finer
spatial and temporal scales will uncover additional interesting relationships.
Furthermore, in addressing the overall pattern, we have averaged out several
major discrete events (e.g., the Exxon Valdez oil spill in 1989) that had
significant consequences for the ecosystem and social system in Alaska (general
EVOS consequences REF). We do not wish to minimize the important of such events,
but note that it is important to understand the benefits of diversification in
the context of rare and extreme disturbances which occur in marine systems
worldwide.

>>>>

Our findings across fishing strategies are in line with previous findings
[@kasperski2013, @sethi2012b, @sethi2014], but we also found that within
strategies, for individuals, specializing tended to be associated with increased
revenue and altering species diversity tended to be associated with increased
revenue variability. Specializing has been shown to be profitable in some
circumstances for other natural resource sectors. For example, while
diversification is generally helpful for small-scale farmers, farmers that
specialize on high-demand and high-value crops such as tobacco or cocoa can
benefit, at least in the short term, from specializing on these crops (REF). In
terms of variance, there are number of reasons by annual revenue variability
might be expected to increase with changes to individual fished species
diversity. First, changes to fishing patterns will sometimes be associated with
a learning or adaptation phase as individuals become accustomed to new
locations, new gear, or new species. Secondly, changes in diversity might
reflect years in which targeted species were less available and fishers were
forced to target other species or landed more bycatch. Most importantly, this
increased variability technically reflects an inability for our large-scale
model to predict an individual's revenue in a subsequent year. There are many
reasons, often unique to an individual permit holder and therefore not included
in a large-scale model, that might make that specific individual's revenue less
predictable given a change in species diversity compared to not changing species
diversity from one year to the next.

Our analysis provides a synthetic view of the effects of species diversity on
individuals over 30 years in one of the most productive fishing regions in the
world. However, this large temporal and geographical scope potentially obscures
time or regional-variation in the consequences of diversification on revenue and
revenue variability. We expect future research examining diversification over
finer scales will uncover additional interesting relationships. Furthermore, in
addressing the overall pattern, we have averaged out several major discrete
events (e.g. the Exxon Valdez oil spill in 1989) that had significant
consequences for the ecosystem and social system in Alaska (REF). In addition to
variability, ... it is important to understand the benefits of diversification
in the context of rare and extreme disturbances which occur in marine systems
worldwide.

@@

Our results provide additional support for the idea that individual fishers can
reduce their income variability by diversifying their catch portfolios. However,
most individuals do not change their catch diversity substantially from year to
year [OLE: is there a supplemental figure or statistic that speaks to this
point?], and most strategies adopted by Alaskan fishermen lie in a high-risk,
high-reward quadrant in which reducing diversification increases both revenue
variability and expected revenue. Previous work has suggested that changes to
fisheries management such as limited entry or catch share programs may
inadvertently act as barrier to diversification and promote specializing
(Hilborn et al. 2003; Kasperski and Holland 2013). While some of these
specialized fishing strategies may be associated with increased revenue
variability, the benefit may be that they are also associated with increased
revenue.

@@

@@
